---
title: rest / stim analysis 
output: "html_document"
---


```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(cowplot)
library(patchwork)
```

Find conserved markers irrespective of the resting versus stimulated condition 

```{r}

#load annotated data
pbmc.combined <- readRDS("pbmc_combined_annotated.rds")

pbmc.combined

table(Idents(pbmc.combined))


# set the default assay to the original "RNA" data, before integration
DefaultAssay(pbmc.combined) <- "RNA"

# find conserved markers
nk.markers <- FindConservedMarkers(pbmc.combined, ident.1 = 1, grouping.var="orig.ident")

head(nk.markers)

```

Count conserved markers with adjusted p-values < 0.05 

```{r}
sel <- nk.markers$rest_p_val_adj < 0.05 & nk.markers$stim_p_val_adj < 0.05
sum(sel)
sum(nk.markers[sel,]$rest_avg_log2FC > 1)
sum(nk.markers[sel,]$rest_avg_log2FC > 2)

```

Plot umap with predicted labels, split rest vs stim

```{r}
DimPlot(pbmc.combined, split.by="orig.ident", group.by="predicted.id", label=T)
```

Feature plot for conserved marker for NK cells SH2D1B versus non specific IFI6  

```{r}
DimPlot(pbmc.combined, group.by="predicted.id",label=T, split.by = "orig.ident", cols=c("#089392", "#13A491", "#40B48B", "#6CC382", "#9DCD84", "#C5D88C", "#EAE29C", "#EACC84", "#EAB672", "#E99F69", "#E6866A", "#E16C72", "#CF597E")) -> p0
FeaturePlot(pbmc.combined, features="SH2D1B", split.by="orig.ident") -> p1
FeaturePlot(pbmc.combined, features="IFI6", split.by="orig.ident") -> p2
FeaturePlot(pbmc.combined, features="CXCL10", split.by="orig.ident") -> p3

p0
p1
p2
p3


#pdf("diff.pdf", width=10,height=21)
#p0/p1/p2/p3
#dev.off()
```


Analyse differentially expressed genes rest vs stim for B cells

```{r}

# set cell identities to predicted classes
Idents(pbmc.combined) <- "predicted.id"
# create new categories combining predicted classes 
pbmc.combined$celltype.stim <- paste(Idents(pbmc.combined), pbmc.combined$orig.ident, sep="_")
# check number of cells per type
table(pbmc.combined$celltype.stim)

# switch cell identities to new category
Idents(pbmc.combined) <- "celltype.stim"

# compare b rest vs b stim
b.ifn.response <- FindMarkers(pbmc.combined, ident.1="B_stim", ident.2 = "B_rest")

# top results
head(b.ifn.response)
# results table size
dim(b.ifn.response)
# results for gene CXCL10
b.ifn.response["CXCL10",]
# count nb of genes with p-value < 0.05
sum(b.ifn.response$p_val_adj < 0.05)
                   
```
